---
title: "Lab HW10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Write a function that calculates cumulative distribution function of a binomial random variable. Compare results from your function with pbinom() function.
```{r}
n <- 100
p <- 0.5
B <- 100000
q <- 50

set.seed(123)
pbinom_manual <- function(q) {
    round(sum(rbinom(B, n, p) <= q) / B, 4)
}

pbinom_manual(q)
round(pbinom(q, n, p), 4)
```
The results using the two methods are very close.

# 2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = ‘one.sample’).
```{r}
B <- 10000
set.seed(123)
power_t_manual <- replicate(B, {
    n <- 30
    x <- rnorm(n, 0.5, 1)
    se <- sd(x) / sqrt(n)
    t <- abs(mean(x) - 0) / se 
    power1 <- ifelse(2 * (1 - pt(t, df = n)) < 0.05, 1, 0)
    power1 
})
power2 <- power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = "one.sample")$power
sum(power_t_manual) / B
round(power2, 4)
```
The results using the two methods are very close.